\resumesection{Experience}
\begin{minipage}[t]{0.95\columnwidth}
    \heading{Texas Instruments - Processors}
    
    \subheadnb{\textbf{ Product Test Engineer } \hfill \textit{06/2023 -- Present}}
    \blurb{
        Develop and execute test plans and validation procedures for silicon devices on Advantest V93000 and Teradyne UltraFLEX Plus ATE platforms. Design, bring up, and qualify multiprobe and final test hardware fixtures. Perform root cause analysis and failure investigation across 28nm, 16nm, 5nm, and 8nm process nodes. Coordinate with overseas assembly/test sites to validate hardware correlation, drive corrective actions, and support product release.
    }
    
    % 0.7em between jobs same employer
    \vspace{0.7em}
    
    \subheadnb{\textbf{ Program Management Engineering} \hfill \textit{01/2025 -- Present}}
    \blurb{
        Coordinate cross-functional teams to drive new silicon designs from validation through market release. Communicate product status, test findings, and risk assessments to internal stakeholders using Jira, SAP, and internal tooling.
    }
    
    % 1.0em between employers
    \vspace{1.0em}
    
    \heading{Texas Tech University - ECE Department}
    
    \subheadnb{\textbf{ Stockroom Employee} \hfill \textit{08/2022 -- 05/2023}}
    \blurb{
    Facilitated in the ordering and selection of electrical components to help students in the completion of their projects in the electrical engineering department.
    }
    
    % 0.7em between jobs same employer

    \vspace{1.0em}
    
    \heading{Textron - Bell Flight}
    
    \subheadnb{\textbf{ Manufacturing Engineer Intern} \hfill \textit{08/2019 -- 03/2020}}
    \blurb{
        Implemented changes to manufacturing documentation to reduce cost using knowledge of fabrication processes, tooling, production equipment, assembly methods, quality control standards, and material usage. Determined root cause of failures through statistical methods and recommended corrective changes to processing methods and planning. CAD software usage for tool modeling and supporting structures used in aerospace manufacturing environments.
    }

\end{minipage}